Thread Management for High Performance Database Systems - Design and Implementation \\{\large Technical Report

### 2018-08-27 Presentations/Paper/paper_thread_pool.tex
Small fix

Parallel data processing can be achieved by different approaches, like instruction and data parallelism or multi threading. We focus on multi threading by implementing a thread pool for the graph database system \textsc{GeckoDB}\footnote{\textsc{GeckoDB} source code repository: \url{https://github.com/geckodb}}. The thread pool will be integrated into \textsc{Bolster}, a high performance library for parallel execution of primitives like for or filter on large data sets. \textsc{Bolster} has similarities to Intel \textsc{Tbb}~\cite{books/daglib/0018624}, a \textsc{C++} template library for parallel programming, but \textsc{Bolster} is written from scratch to perfectly fit into \textsc{GeckoDB}s specialized storage engine and vectorized query engine, both written in C11~\cite{pinneckegridtables}.

>>>>

Parallel data processing can be achieved by different approaches, like instruction and data parallelism or multi threading. We focus on multi threading by implementing a thread pool for the graph database system \textsc{GeckoDB}\footnote{\textsc{GeckoDB} source code repository: \url{https://github.com/geckodb}}. The thread pool will be integrated into \textsc{Bolster}, a high performance library for parallel execution of primitives like \textit{for}-loops, or \textit{filter}-operation on large data sets. \textsc{Bolster} has similarities to Intel \textsc{Tbb}~\cite{books/daglib/0018624}, a \textsc{C++} template library for parallel programming, but \textsc{Bolster} is written from scratch to perfectly fit into \textsc{GeckoDB}s specialized storage engine and vectorized query engine, both written in C11~\cite{pinneckegridtables}.
